Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-09 publication_materials/ms_rbc.tex
intro/abstract rev2c

\begin{abstract}
Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number limit.
In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated solutions and analyze their properties. 
We compare these solutions with statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulations; marginally-stable thermally-equilibrated states have thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$. 
We initialize 2-dimensional simulations with solutions to the quasilinear problem; they do not undergo a convective transient period and are kinetically exaggerated.
\end{abstract}

@@

\section{Introduction}
Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows.

The simulation of aggressive convection, which is associated with large Rayleigh numbers $Ra$, is expensive. 
State of the art convection simulations performed by \cite{Zhu} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
The scaling behavior of the Nusselt number $\Nu$ (convective strength) in the highly turbulent ultimate regime is of particular interest.
There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}.

Reduced models are particularly useful in this context because they allow us to study the system with relatively low expense. 
Much of the published work on this topic relates to unstable time-invariant solutions \cite{Waleffe}, \cite{Sondak}, \cite{Wen}, \cite{chini_cells}. 
Simulations and analysis performed by \cite{Yalniz} and \cite{Cvitanovic} suggest that chaotic solution trajectories can be modelled as a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of time-invariant unstable solutions. Should that be the case, it is crucial that we discover and classify such time-invariant solutions.

In \cite{Chini_sw}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. This is realized by defining a mean state, which which is marginally stable, then analytically deriving an equation for then first-order perturbations' amplitude. 
In this investigation, we seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.

@@

>>>>

\begin{abstract}
Natural convection is ubiquitous throughout the physical sciences and engineering, yet many of its important properties remain elusive -- particularly in the large Rayleigh number regime.
In this investigation, we derive and solve a quasilinear form of the Boussinesq Rayleigh-B\'enard equations. 
Eigenfunction amplitudes are obtained by requiring marginal-stability. We obtain symmetric thermally-equilibrated solutions and analyze their properties. 
Solutions to the quasilinear problem differ from statistically-steady 2-dimensional Rayleigh-Be\'nard convection simulation data, having thinner boundary layers and larger Nusselt numbers $\Nu$ which scale like $\Nu \sim Ra^{1/3}$. 
We initialize 2-dimensional simulations with solutions to the quasilinear problem; they do not undergo a convective transient period and are kinetically exaggerated.
\end{abstract}

@@

\section{Introduction}
Rayleigh-B\'enard convection plays a foundational role in large-scale astrophysical and geophysical settings.
Buoyancy-driven convection regulates heat transfer and often gives way to violently turbulent flows, thereby dominating the large-scale behaviors and fueling small-scale processes \cite{Couston} in important systems.

Aggressive convection, which is associated with large Rayleigh numbers $Ra$, is difficult to simulate. 
State of the art convection simulations performed by \cite{Zhu} have reached $Ra = 10^{14}$ but estimates for stars are $Ra \sim 10^{20}$ \cite{Ossendrijver}. 
The scaling behavior of the Nusselt number $\Nu$ (nondimensionalized heat transfer) in the highly turbulent ultimate regime is of particular interest.
There exists a substantial body of work pertaining to this specific topic with no general consensus \cite{Malkus}, \cite{Kraichnan} \cite{Spiegel}, \cite{Castaing}, \cite{Grossman}, \cite{Ahlers}.

Reduced models are particularly useful in this context because they allow us to study the problem with relatively low expense. 
Much of the published work on this topic relates to unstable coherent solutions \cite{Waleffe}, \cite{Sondak}, \cite{Wen}, \cite{chini_cells}. 
Simulations and analysis performed by \cite{Yalniz} and \cite{Cvitanovic} suggest that chaotic solution trajectories can be modelled as a Markov chain whose long-term behavior is given by the time-weighted-average of a finite set of unstable coherent solutions. Should that be the case, it is crucial that we discover and classify such states.

In \cite{Chini_sw}, researchers develop and solve a quasilinear formulation of the Navier-Stokes equations via multi-scale asymptotic arguments. This is realized by defining a mean state which hypothetically evolves on a slow time-scale. An analytic expression for the first-order perturbations' amplitude is found by deriving a solvability condition of the second-order perturbations and integrating over the domain spatially. 
We seek to solve the Boussinesq Rayleigh–Bénard convection equations using an analogous strategy. 
The application of this procedure yields time-invariant solutions to the quasilinear problem with a range of expected and unexpected features.

@@

\bibitem{Couston} Couston, L.A., Lacoanet, D., Favier, B., Bars, M. (2019). Shape and size of large-scale vortices: a universal fluid pattern in geophysical dynamics
